Competition

### 2020-10-05 R/competition wrangling.Rmd
added some combined annuli because it was easier than figuring out how to do a weighted average after the fact.
added se to marginal effects function.  Moved euclidean distance functiuon.

```{r}
# function to calculate euclidean distance between two points
eu_dist <- function(p1, p2) {
  sqrt(sum((p1 - p2)^2))
}
# x = c(0,0)
# y = c(3,3)
# eu_dist(x, y)
```

@@

```{r}
ha_density <-
  ha_xy %>% 
  group_by(plot, year) %>% 
  group_split() %>% 
  # head() %>% #test with 6 df to see how long it will take.
  future_map(~{
      add_density_cols(.x, L = 0, U = 5, by = 0.5) 
    }) %>% 
  bind_rows()
beepr::beep(4)
```

>>>>

@@

```{r}
ha_density <-
  ha_xy %>% 
  group_by(plot, year) %>% 
  group_split() %>% 
  # head() %>% #test with 6 df to see how long it will take.
  future_map(~{
    add_density_cols(.x, L = 0, U = 5, by = 0.5)
  }) %>% 
  future_map(~{
    add_density_cols(.x, L = 0, U = 5, by = 2.5)
  }) %>% 
  bind_rows()
beepr::beep(4)
```
